---
title: "Analyze shortcut effects"
author: "Zining Zhu"
date: "12/17/2021"
output: html_document
---

## Load data
(Loading the bigram_shift as example. Will repeat for other SentEval tasks later.)
```{r}
library(lme4) 
library(lmerTest)

df <- rbind(
  read.csv("../reports/report_bigram_shift.roberta.csv"),
  read.csv("../reports/report_coordination_inversion.roberta.csv"),
  read.csv("../reports/report_obj_number.roberta.csv"),
  read.csv("../reports/report_odd_man_out.roberta.csv"),
  read.csv("../reports/report_past_present.roberta.csv"),
  read.csv("../reports/report_subj_number.roberta.csv"))
head(df)
```

```{r}
df_fvz = df[(df$config=='Full') | (df$config=='ZeroMI'),]
df_nvz = df[(df$config=='Nonzero') | (df$config=='ZeroMI'), ]
df_fvn = df[(df$config=='Full') | (df$config=='Nonzero'),]
```

Linear mixture model.

```{r}
model_fvz <- lm(test_acc ~ task + model + config, data=df_fvz)
anova(model_fvz)
model_nvz <- lm(test_acc ~ task + model + config, data=df_nvz)
anova(model_nvz)
model_fvn <- lm(test_acc ~ task + model + config, data=df_fvn)
anova(model_fvn)
```
In both Full vs ZeroMI (`fvz`) and Nonzero vs ZeroMI (`nvz`) settings, the configuration has significant effects on the test accuracy; but the config has no effects in Full vs Nonzero (`fvn`) setting.

## LMM with random effects
```{r}
model_fvn_re <- lmer(test_acc ~ task + model + config + (1+config|rs), data=df_fvn)
anova(model_fvn_re)
```
```{r}
model_fvn_re <- lmer(test_loss ~ task + model + config + (1+config|rs), data=df_fvn)
anova(model_fvn_re)
```

When considering the random effects of the seeds, the config still has no effects.
